PK object batch mode trial

### 2023-08-02 data-raw/batchMode_trial_gpm.Rmd
Updated several methods to work with data_groups that were unable to be fit. Some methods ignore these (get_tkstats) while others are supplied NAs (plot)

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
                subjects.species_harmonized %in% "hamster",
                studies.administration_route_normalized %in% "iv")
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9021924")

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID2021103")
# Opt params not found ERROR
# 
#

@@

```{r remaining_methods}
# coef_sd

devtools::load_all()
AIC(my_pk2) %>% View()
BIC(my_pk)

@@

my_hess <- coef_sd(my_pk)

my_hess %>%
  rowwise() %>%
  mutate(sds = list(sds))

>>>>

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
                subjects.species_harmonized %in% "hamster",
                studies.administration_route_normalized %in% "iv")
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9030258")

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID7030066",
                                                              "DTXSID0020442",
                                                              "DTXSID2021315"),
                subjects.species_harmonized %in% "rat")

@@

```{r remaining_methods}
devtools::load_all()
AIC(my_pk2) %>% View()
BIC(my_pk)

@@

my_hess <- coef_sd(my_pk, table_format = TRUE)

ggplot(inner_join(get_winning_model(my_pk), my_hess),
       aes(x = Fgutabs,
           y = V1)) +
  geom_point() +
  facet_grid(cols = vars(model))
